### 2019-10-11 paper/conclusion.tex

\section{Conclusion}

In the present paper, five different types of initial fissile materials have been studied for transitioning to thorium fuel cycle in the \gls{SD-TMSR}. The molar composition of startup fuel for all five cases is listed in Table~\ref{tab:table4}, as well, the inventories in Table~\ref{tab:table5}. We adopted two different feed mechanisms; thorium feed mechanism and non-thorium feed mechanism. The whole-core of the SD-TMSR was simulated with Pu reactor-grade, TRU, and $^{233}$U as initial fissile materials. Besides, the variation of the effective multiplication factor $k_{eff}$, inventory, and other neutronic parameters have been investigated. Results demonstrated that continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel. Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U. in addition, the Pu proportion in fuel salt has been calculated and found to be below the solubility limit. Finally, the neutron flux spectrum for the three selected cases has been described.

\section{Future work}

%The authors intend to compare the present results and results from SaltProc batch-wise code \cite{rykhlevskii2019modeling} in future work. Moreover, they will consider the delayed neutron precursor drift. Future work will also consider the benchmark study based on other codes and models. The authors intend to conduct a sensitivity study to evaluate the impact of the radial reflector material and its thickness. In addition, they will study the impact of \gls{FPs} removal (i.e. only reprocessing without refueling) on reactivity and neutron economy.

>>>>

\section{Conclusion} \label{Conclusion}

Five different types of initial fissile loadings have been studied for 
transitioning to the thorium fuel cycle in the \gls{SD-TMSR}. We 
adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
performed with Pu reactor-grade, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

Results demonstrated that continuous flow of Pu reactor-grade allows the 
transition to the thorium fuel cycle in a relatively short time ($\approx$ 
$4.5$ years) compared to $26$ $years$ for Th/$^{233}$U startup fuel. 
Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility 
of operating the SD-TMSR for an extended time ($\approx$ $40$ $years$) 
without any external feed of $^{233}$U. Notably, the Pu mass fraction in 
fuel salt was calculated and found to be below the solubility limit.

Additionally, the neutron energy spectrum shift during the reactor operation 
for the Pu and TRU cases is different from the $^{233}$U fueling scenario. 
Indeed, the spectrum hardening for $^{233}$U initial fissile isotope during 
operation, but softening for the Pu and TRU cases. Notably, the most 
significant neutron energy spectrum shift was obtained for reactor-grade Pu 
startup loading.

We compared the operational and safety parameters of the \gls{SD-TMSR} for all 
three startup fuels at both initial and equilibrium states. The total 
temperature coefficient of reactivity is negative and relatively large in all 
cases. For TRU case, the coefficient remained almost constant during 
operation: $-4.79\pm0.12$ $pcm/K$ and $-4.76\pm0.11$ $pcm/K$ for the initial 
and equilibrium states, respectively. For reactor-grade Pu, the coefficient 
absolute value decreased from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
60 years of operation. Finally, the six factors evolution during the operation 
were calculated for all three cases, and these parameters can be used to 
design the reactivity control system of the \gls{SD-TMSR}.

\section{Future work}
The authors intend to verify obtained results using another tool: batch-wise 
code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
Moreover, in further simulations, we intend to take into account the delayed 
neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
been introduced in the literature yet. Thus, the control rods design and 
configuration might be suggested in the nearest future.

Lastly, an additional area to explore is the accident safety analysis which 
requires high-fidelity multi-physics model of the \gls{SD-TMSR} with the 
coupled neutronics/thermal-hydraulics software, Moltres 
\cite{lindsay_introduction_2018}. The full-core SERPENT-2 model of the 
\gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in this work, 
would be employed to generate problem-oriented nuclear data libraries for 
Moltres. The ultimate goal of this effort is to develop a 
fast-running computational model for studying the dynamics behavior of generic 
\glspl{MSR}, performing safety analysis for different accident scenarios and 
optimizing design of various reactor concepts.

### 2019-10-11 paper/methods.tex

\begin{table}  %[!ht]
	\caption{Reactor-grade plutonium vector (Mass fraction \%) \cite{marka1993explosive}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		 1.3&60.3&24.3&9.1&5 \\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\begin{table}  %[!ht]
	\caption{\gls{TRU} vector (Mass fraction \%) \cite{de2000scenarios}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s s s s s}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table3}
\end{table}

For reactor-grade plutonium case, the composition was taken for plutonium 
recovered from the spent fuel composition of commercial \gls{PWR} with the 
average discharge burnup $33$ $GWd/t$ and after $10$ years of cooling before 
reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
isotopic compositions of \gls{TRU} was taken for the SF of UOX \gls{PWR} 
(after one use, no multi-recycling) with the average discharge $60$ 
$GWd/t$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
The molar composition of start-up fuel for all five cases is listed in 
Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei 
inventories with different types of fuel are summarized in 
Table~\ref{tab:table5}.
\begin{table}  %[!ht]
	\caption{Composition of start-up fuel (mole\%)}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.16\textwidth} X p{0.17\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt\%) 
		& Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		LiF&70&70&70&70&70\\
		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
		ThF$_4$&8.25&7.5&10.75&	8.65&12.3		\\
		UF$_4$&4.25&4.75&&&	0.2		\\
		PuF$_3$&&0.25&1.75&&		\\
		(TRU)F$_3$&&&	&3.85	&\\
		\hline
	\end{tabularx}
	\label{tab:table4}
\end{table}

\begin{table}  %[!ht]
	\caption{Initial nuclei inventories (in grams) of the SD-TMSR with different types of fuel.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s}
		\hline
		\vspace{0.1in}
		Molecule& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		$^{232}$Th       &6.24E+07 & 4.67E+07 &   6.75E+07			& 5.44E+07	& 7.69E+07    \\ 
		$^{233}$U        &         & &        &       &  1.30E+06 \\
		$^{235}$U        & 3.17E+06 &6.01E+06	&            &   & \\
		$^{238}$U      	 &1.28E+07  &2.43E+07 &	&  &\\
		$^{237}$Np	  	 &         && &1.58E+06	&    \\
		$^{238}$Pu	  	 &         &1.60E+04	& 1.13E+05 & 6.78E+05	&   \\
		$^{239}$Pu       &         &9.59E+05&6.76E+06& 1.15E+07&    \\
		$^{240}$Pu       &         &3.99E+05& 2.82E+06&5.40E+06&  	\\  
		$^{241}$Pu		 &         &1.60E+05&1.13E+06&2.69E+06&   \\
		$^{242}$Pu		 &         &6.39E+04	&4.51E+05	& 1.68E+06& \\
		$^{241}$Am		 &         &&& 8.53E+05 & \\
		$^{242}$Am		 &         &&&  &\\
		$^{243}$Am       &        & &&4.77E+05&\\
		$^{244}$Cm		 &        & &&2.01E+05&  \\
		$^{245}$Cm		 &        & &&			2.51E+04	&   \\
		&         &&		&		&\\
		Total mass \\of HM without $^{232}$Th	& 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  \\
		\hline
	\end{tabularx}
\label{tab:table5}
\end{table}

>>>>

\begin{table}  %[!ht]
	\caption{Reactor-grade plutonium vector (wt.\%) \cite{marka1993explosive}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		 1.3&60.3&24.3&9.1&5 \\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\begin{table}  %[!ht]
	\caption{\gls{TRU} vector (wt.\%) \cite{de2000scenarios}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s s s s s}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table3}
\end{table}

For reactor-grade plutonium case, the composition was taken for plutonium 
recovered from the spent fuel composition of commercial \gls{PWR} with the 
average discharge burnup $33$ $GWd/t$ and after $10$ years of cooling before 
reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
isotopic compositions of \gls{TRU} was taken for the SF of UOX \gls{PWR} 
(after one use, no multi-recycling) with the average discharge $60$ 
$GWd/t$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
The molar composition of start-up fuel for all five cases is listed in 
Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei 
inventories with different types of fuel are summarized in 
Table~\ref{tab:table5}.
\begin{table}  %[!ht]
	\caption{Composition of startup fuel (mole\%).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.13\textwidth} X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) 
		& Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		LiF&70&70&70&70&70\\
		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
		ThF$_4$&8.25&7.5&10.75&	8.65&12.3		\\
		UF$_4$&4.25&4.75&&&	0.2		\\
		PuF$_3$&&0.25&1.75&&		\\
		(TRU)F$_3$&&&	&3.85	&\\
		\hline
	\end{tabularx}
	\label{tab:table4}
\end{table}

\begin{table}  %[!ht]
	\caption{Initial heavy metal inventories (excluding $^{232}$Th) for 
	different initial fissile loadings (g).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{X X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Nuclide & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) & Pu 
		reactor-grade & \gls{TRU}& $^{233}$U \\	\hline
		$^{232}$Th       &6.24E+07 & 4.67E+07 &   6.75E+07			& 5.44E+07	& 7.69E+07    \\ 
		$^{233}$U        &         & &        &       &  1.30E+06 \\
		$^{235}$U        & 3.17E+06 &6.01E+06	&            &   & \\
		$^{238}$U      	 &1.28E+07  &2.43E+07 &	&  &\\
		$^{237}$Np	  	 &         && &1.58E+06	&    \\
		$^{238}$Pu	  	 &         &1.60E+04	& 1.13E+05 & 6.78E+05	&   \\
		$^{239}$Pu       &         &9.59E+05&6.76E+06& 1.15E+07&    \\
		$^{240}$Pu       &         &3.99E+05& 2.82E+06&5.40E+06&  	\\  
		$^{241}$Pu		 &         &1.60E+05&1.13E+06&2.69E+06&   \\
		$^{242}$Pu		 &         &6.39E+04	&4.51E+05	& 1.68E+06& \\
		$^{241}$Am		 &         &&& 8.53E+05 & \\
		$^{242}$Am		 &         &&&  &\\
		$^{243}$Am       &        & &&4.77E+05&\\
		$^{244}$Cm		 &        & &&2.01E+05&  \\
		$^{245}$Cm		 &        & &&			2.51E+04	&   \\ \hline
		Total            & 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  
		\\
		\hline
	\end{tabularx}
\label{tab:table5}
\end{table}
